Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-07 manuscript.tex
6 updates

The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7. 
This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
The combined results for all the stars considered are displayed in Fig.~\ref{fig:se}. 
The top plots show the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). 
In the bottom plots show the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise than the Normal parameters, respectively.

Looking at the estimates for the RV, we see that they all follow a similar exponential decay. Although we plot the data for three different stars, we do not see any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV. This is not surprising as the three stars studied here are all main sequence K-dwarfs.

When comparing the three different estimates for the RV, we see that SN mean RV presents standard errors that are 60\% larger than what N mean RV gives. On the opposite, SN median RV gives errors 10\% more precise than N mean RV. Regarding the parameters describing the width of the CCF, FWHM and SN FWHM have the same standard errors. Finally, for the asymmetry parameters, we see that $\gamma$, derived from the SN, is 15\% more precise than BIS SPAN. In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV, we are able to improve by 10\% the precision on the RV, 15\% the precision on the asymmetry, and this without degrading the precision on the width estimate. SN mean RV should not be use to derive precise RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived when using the mean of a Normal density fit to the CCF.
%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameters. When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved when fitting a Normal density (red triangles). However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. The use of the asymmetry SN parameter $\gamma$ leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN. Note that for the asymmetry, the error in BIS SPAN is in \ms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
   \label{fig:se}
\end{center}
\end{figure*}

>>>>

The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7. \jessi{Why weren't the others stars included?}
This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
The combined results for all the stars considered are displayed in Fig.~\ref{fig:se}. 
The top plots show the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). 
In the bottom plots show the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise than the Normal parameters, respectively.

The estimates for the RV all appear to follow a similar exponential decay. Although the results for three different stars are included in the plot, there do not appear to be any offsets in this decay, which implies that the SNR at 550 nm is the main contributor to the precision measured in RV. \jessi{The previous sentence does not make sense to me.  Why would no offsets imply it is the main contributor in the precision?}
This is not surprising as the three stars studied here are all main sequence K-dwarfs.

When comparing the three different estimates for the RV, the SN mean RV presents standard errors that are 60\% larger than the N mean RV. However, the SN median RV gives errors 10\% more precise than N mean RV. 
Regarding the parameters describing the width of the CCF, FWHM and SN FWHM have the same standard errors. Finally, for the asymmetry parameters, we see that $\gamma$, derived from the SN, is 15\% more precise than BIS SPAN. In conclusion, when fitting a SN density to the CCF and using as RV estimates SN mean RV, we are able to improve by 10\% the precision on the RV, 15\% the precision on the asymmetry, and this without degrading the precision on the width estimate. SN mean RV should not be use to derive precise RVs, except perhaps in specific conditions described below, as the precision on this parameter is 60\% worse than the precision on the RVs derived when using the mean of a Normal density fit to the CCF.
%
\begin{figure*}[htbp]
\begin{center}
\includegraphics[height = 6in]{[5]Errors_vs_SNR_all_stars.pdf} 
   \caption{Comparison between the standard errors using the bootstrap analysis for the RVs, the FWHM and the asymmetry parameters. When using SN mean RV (black circles), the standard errors are in average $60\%$ larger than the standard errors retrieved when fitting a Normal density (red triangles). However, if using SN median RV (cyan crosses), the standard errors are in average $10\%$ smaller than the standard errors coming from the Normal fit. The use of the asymmetry SN parameter $\gamma$ leads to standard errors in average $15\%$ smaller than the standard errors related to the BIS SPAN. Note that for the asymmetry, the error in BIS SPAN is in \ms. To be able to compare the errors in $\gamma$ and BIS SPAN, we multiplied the error in $\gamma$ by the slope of the correlation between $\gamma$ and BIS SPAN.}
   \label{fig:se}
\end{center}
\end{figure*}
